---
title: "A glimpse of the hubr package"
author: "L. Vaudor"
date: "27 novembre 2018"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(33)
```

```{r, warning=FALSE, message=FALSE}
library(hubr)
```

Let us consider the following signal, which is composed of several segments with differing lengths and means (but constant variance):

```{r, fig.width=6, fig.height=4}
x=c(rnorm(130,3,2),
    rnorm(220,10,2),
    rnorm(500,2,2),
    rnorm(50,-4,2),
    rnorm(30,2,2),
    rnorm(120,8,2))
plot(x, type="l")
```

The `Hubert_segmentation()` function detects automatically the breaks in this shifting means signal:


```{r, fig.width=6, fig.height=4}
seg_obj=Hubert_segmentation(x)
plot(x, type="l")
lines(model_signal(x,seg_obj$locations), col="red",lwd=3)
```

`model_signal()` is a helper function which returns the series of predicted values according to the segmentation object.



Now, let us consider a signal with shifting means, in which the shift in mean is a bit less important when compared to variance.

```{r, fig.width=6, fig.height=4}
x=c(rnorm(130,3,2),
    rnorm(220,5,2),
    rnorm(500,4,2),
    rnorm(50,6,2),
    rnorm(30,4,2),
    rnorm(120,3,2))
plot(x, type="l")
```

```{r, fig.width=6, fig.height=4}
seg_obj=Hubert_segmentation(x)
plot(x, type="l")
lines(model_signal(x,seg_obj$locations), col="red",lwd=3)
```

